Abstract Plots

### 2021-07-29 Abstract.Rmd
Final changes to supplementary table.

#vector indicating dilution amount
percent.FFPE = rep(c("10%", "30%", "50%", "70%", "90%"),
                   length(signature.names)*iteration.num)
#vectorize lists
signature = unlist(signature)
sens = unlist(sens)
spec = unlist(spec)

#convert into data frame
table = data.frame(percent.FFPE, signature, sens, spec)

#avg the multiple sensitivity/specificity values for each dilution and each signature
table <- table %>%
  group_by(percent.FFPE, signature) %>%
  summarize(sens = mean(sens, na.rm = TRUE),
            spec = mean(spec, na.rm = TRUE),
            acc = mean(acc, na.rm = TRUE))
```

>>>>

#vector indicating dilution amount
percent.FFPE = rep(c("10%", "30%", "50%", "70%", "90%"),
                   length(signature.names)*iteration.num)
#vectorize lists
signature = unlist(signature)
acc = unlist(acc)
sens = unlist(sens)
spec = unlist(spec)

#convert into data frame
table = data.frame(percent.FFPE, signature, sens, spec, acc)

#avg the multiple sensitivity/specificity values for each dilution and each signature
table <- table %>%
  group_by(percent.FFPE, signature) %>%
  summarize(sens = mean(sens, na.rm = TRUE),
            spec = mean(spec, na.rm = TRUE),
            acc = mean(acc, na.rm = TRUE)) %>%
  mutate(signature = factor(signature, signature.names)) %>%
  arrange(signature)
```
